---
title: "Retail Analysis with Walmart Data"
output:
  html_document: default
  pdf_document: default
date: '2022-04-05'
---
### Uploading and Reading the Dataset
```{r}
Wdf = read.csv("~/SimpliLearn Data Analytics/Chapter 4 Data Science with R/Walmart_Store_sales.csv")
```

### Data Description
```{r}
View(Wdf)
str(Wdf)
head(Wdf)
class(Wdf)
```

### Descriptive Statistics
```{r}
summary(Wdf)
```

### Checking NA values 
```{r}
colSums(is.na(Wdf)) 
```
##### No null values in the dataset


### Loading all the needed libraries
```{r}
library("dplyr")
library("lubridate")
library("zoo")


#Data Visualization
library("grid")
library("vcd")
library("ggplot2")
library("plotly")

```


### Converting Date column into Date format also, converting Store and Holiday Flag column into Factor
```{r}
Wdf$Date = as.Date(Wdf$Date,format="%d-%m-%Y")
Wdf$Store = as.factor(Wdf$Store)
Wdf$Holiday_Flag = as.factor(Wdf$Holiday_Flag)
```

### Q1- which store has max sales?
```{r}
store_sales = aggregate(Weekly_Sales~Store,data=Wdf, sum)
store_sales
which.max(store_sales$Weekly_Sales) 
store_sales[20,]
```
#### A-Store 20 has highest sale, sale value of 301397792



### Q2- Which store has maximum standard deviation i.e., the sales vary a lot?
```{R}
store_sales$sales_mean = aggregate(Weekly_Sales~Store,data=Wdf, mean)$Weekly_Sales
store_sales$sales_sd = aggregate(Weekly_Sales~Store,data=Wdf, sd)$Weekly_Sales
str(store_sales)
arrange(store_sales, desc(sales_sd))
```
#### A-Store 14 has highest standard deviation = 317569.95

### Q3- Which store/s has good quarterly growth rate in Q3'2012?
```{r}
# creating copy of Wdf 
Wdf2 = Wdf

Wdf2$month_Year = substr(Wdf2$Date, 1, 7)
Q3_2012 = filter(Wdf2,month_Year == "2012-07" | month_Year== "2012-08" | month_Year== "2012-09")
Q2_2012 = filter(Wdf2,month_Year == "2012-04" | month_Year== "2012-05" | month_Year== "2012-06")

#Aggregating sales by store for Q3-2012 
Q3_2012_Sales = summarise(group_by(Q3_2012,Store),sum(Weekly_Sales))

#Aggregating sales by store for Q3-2012 
Q2_2012_Sales = summarise(group_by(Q2_2012,Store),sum(Weekly_Sales))

Q3_2012_Growthrate = merge ( Q2_2012_Sales , Q3_2012_Sales , by = 'Store')
Q3_2012_Growthrate = mutate(Q3_2012_Growthrate, Growth_Rate = ((Q3_2012_Sales$`sum(Weekly_Sales)` - Q2_2012_Sales$'sum(Weekly_Sales)')*100) / Q2_2012_Sales$'sum(Weekly_Sales)')
gr = arrange(Q3_2012_Growthrate, desc(Growth_Rate))
View(gr)
```
#### A- Store 15 has highest growth rate in Q3 2012

### Q4- Some holidays have a negative impact on sales.Find out holidays which have higher sales than the mean sales in non-holiday season for all stores together
```{r}
SuperBowl = as.Date(c("2010-02-12","2011-02-11","2012-02-10","2013-02-08"))
LabourDay = as.Date(c("2010-09-10", "2011-09-09", "2012-09-07", "2013-09-06"))
Thanksgiving = as.Date(c("2010-11-26", "2011-11-25", "2012-11-23", "2013-11-29"))
Christmas = as.Date(c("2010-12-31", "2011-12-30", "2012-12-28", "2013-12-27"))

Walmart_Holiday = Wdf[1:3] 

Walmart_Holiday$hflag = ifelse(Walmart_Holiday$Date %in% SuperBowl, "SB", ifelse(Walmart_Holiday$Date %in% LabourDay, "LD", ifelse(Walmart_Holiday$Date %in% Thanksgiving, "TG", ifelse(Walmart_Holiday$Date %in% Christmas, "CH","None"))))
aggregate(Weekly_Sales~hflag,data=Walmart_Holiday, mean)
```
#### A- Thanks giving have highest sales than mean. Mean sales in non-holiday season for all stores together is 1041256.4 and except Christmas all holidays have higher sales than average sale in non-holiday sale.

### Q5- Provide a monthly and semester view of sales in units and give insights
```{r}
semester_view = Wdf
View(semester_view)
semester_view_month_year = transform(semester_view,Year_Sale = as.numeric(format(Date,"%Y")),Month_Sale = as.numeric(format(Date,"%m")))
View(semester_view_month_year)

Summarized_View = aggregate(Weekly_Sales~Month_Sale+Year_Sale,semester_view_month_year,sum)
View(Summarized_View)

Insights = arrange(Summarized_View,desc(Weekly_Sales))
View(Insights)
```
#### A- The sales are highest in December and Lowest in January and are  higher in second semester of every year



### For Store 1 – Build  prediction models to forecast demand
#### Linear Regression – Utilize variables like date and restructure dates as 1 for 5 Feb 2010 (starting from the earliest date in order). Hypothesize if CPI, unemployment, and fuel price have any impact on sales.
```{r}
library(dplyr)
semester_viewtore1 = select(filter(Wdf, Store==1),-1) ## Filtering data for Store 1 for building linear model
View(semester_viewtore1)
str(semester_viewtore1)
## Linear Model
Wdf_lm = lm(Weekly_Sales ~ Holiday_Flag + Temperature + Fuel_Price+ CPI + Unemployment , semester_viewtore1)
summary(Wdf_lm)

## Drop most insignificant variables- Unemployment and Fuel Price (p value = 60.80%)
Wdf_lm1 = lm(Weekly_Sales ~ Holiday_Flag + Temperature ++ CPI , semester_viewtore1)
summary(Wdf_lm1)

## Drop most insignificant variable Holiday_Flag1 (p value = 5.15%)
Wdf_lm3 = lm(Weekly_Sales ~ Temperature + CPI , semester_viewtore1)
summary(Wdf_lm3)
```
#### We can say only CPI and Temperature are the Variables we can use to build a model as other variables are insignificant

### Model can be further improvised by-
1-Considering all Stores data for prediction

2-Using Advanced models like Decision Trees, Random Forest

3-Using K cross validation techniques for Sampling data


### Change dates into days by creating new variable
```{r}
Data2 = Wdf
Data2$Weekdays = weekdays(Data2$Date)
View(Data2)
```

